Properties and Bayesian fitting of restricted Boltzmann machines

### 2017-11-30 writing/paper-rbm/docs/paper_blinded.tex
submission 2

\title{\bf Properties and Bayesian fitting of restricted Boltzmann machines}
\author{Andee Kaplan \\ Department of Statistical Science, Duke University \\  and \\ Daniel Nordman \\ Department of Statistics, Iowa State University \\  and \\ Stephen Vardeman \\ Department of Statistics and Department of Industrial and\\
Manufacturing Systems Engineering, Iowa State University \\ }

@@

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in Kaplan, Nordman, and Vardeman
(\protect\hyperlink{ref-kaplan2016propriety}{2016}). These findings also
have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, we do not limit consideration to exponential family forms
with a fixed number of parameters.

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
Kaplan, Andee, Daniel Nordman, and Stephen Vardeman. 2016. ``On the
Propriety of Restricted Boltzmann Machines.'' \emph{arXiv Preprint
arXiv:1612.01158}.

@@

>>>>

\bigskip
\bigskip
\bigskip
%\begin{center}
  %{\LARGE\bf Title}
  \title{\bf Properties and Bayesian fitting of restricted Boltzmann machines}
%\end{center}
\medskip

@@

In other words, S-unstable RBM model sequences are guaranteed to stack
up all probability on a specific set of outcomes for visibles, which
could potentially be arbitrarily narrow. Proofs of Propositions
\ref{prp:instab1} and \ref{prp:degen} follow from more general results
in XXX (\protect\hyperlink{ref-kaplan2016propriety}{2016}). These
findings also have counterparts in results in Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), but unlike
results there, we do not limit consideration to exponential family forms
with a fixed number of parameters.

@@

@@

\leavevmode\hypertarget{ref-kaplan2016propriety}{}%
XXX, XXX. 2016. ``On the Propriety of Restricted Boltzmann Machines.''

### 2017-11-30 writing/paper-rbm/index.Rmd
submission 2

---
title: "Properties and Bayes fitting of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Department of Industrial and
      | Manufacturing Systems Engineering
site: bookdown::bookdown_site
output: 
  bookdown::pdf_book:
    includes:
      in_header: ../resources/latex/header.tex
    toc: no
bibliography: [../resources/latex/refs_rbm.bib]
github-repo: andeek/rbm
abstract: |
   A restricted Boltzmann machine (RBM) is an undirected graphical model constructed for discrete or continuous random variables, with two layers, one hidden and one visible, and no conditional dependency within a layer. In recent years, RBMs have risen to prominence due to their connection to deep learning. By treating a hidden layer of one RBM as the visible layer in a second RBM, a deep architecture can be created. RBMs are thought to thereby have the ability to encode very complex and rich structures in data, making them attractive for supervised learning. However, the generative behavior of RBMs is largely unexplored. In this paper, we discuss the relationship between RBM parameter specification in the binary case and model properties such as degeneracy, instability and uninterpretability. We also describe the difficulties that arise in likelihood-based and Bayes fitting of such (highly flexible) models, especially as Gibbs sampling (quasi-Bayes) methods are often advocated for the RBM model structure.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---

>>>>

---
title: "Properties and Bayesian fitting of restricted Boltzmann machines"
author: 
  - name: Andee Kaplan
    university: Duke University
    department: Department of Statistical Science
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Department of Industrial and
      | Manufacturing Systems Engineering
site: bookdown::bookdown_site
output: 
  bookdown::pdf_book:
    includes:
      in_header: ../resources/latex/header.tex
    toc: no
bibliography: [../resources/latex/refs_rbm.bib]
github-repo: andeek/rbm
abstract: |
   A restricted Boltzmann machine (RBM) is an undirected graphical model constructed for discrete or continuous random variables, with two layers, one hidden and one visible, and no conditional dependency within a layer. In recent years, RBMs have risen to prominence due to their connection to deep learning. By treating a hidden layer of one RBM as the visible layer in a second RBM, a deep architecture can be created. RBMs are thought to thereby have the ability to encode very complex and rich structures in data, making them attractive for supervised learning. However, the generative behavior of RBMs is largely unexplored. In this paper, we discuss the relationship between RBM parameter specification in the binary case and model properties such as degeneracy, instability and uninterpretability. We also describe the difficulties that arise in likelihood-based and Bayes fitting of such (highly flexible) models, especially as Gibbs sampling (quasi-Bayes) methods are often advocated for the RBM model structure.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---
